Secure Composition of Robust and Optimising Compilers

### 2023-07-06 popl/main.tex
Add conclusion and acks

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
\end{acks}

>>>>

This paper does a first step towards practical secure compilation chains by introducing a theoretical framework demonstrating that secure compilers compose.
The paper exercises this framework on a case-study that consists of an optimizing compilation chain that is secure with respect to \gls{msscct}.
In future work, it would be interesting to investigate wether it is possible to provide {\em secure compiler combinators}, similarily to how parser combinators work.
%To this end, it may be necessary to extend existing frameworks for multi--language semantics.
It is also interesting to extend our case--study and verify all results of it in Coq.
This way, it is possible to obtain an executable, secure compiler.
However, the formalization effort for backtranslation proofs is known to be enormous, so another research avenue may be to find better ways to (semi-)automate standard secure compilation proofs.

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
  We would like to thank the anonymous reviewers for their feedback.
\end{acks}
